# Ineqaulity task - week 4

### Read in data:

Located within the Data folder:

-   HDI data from: <https://hdr.undp.org/data-center/documentation-and-downloads>
-   Shapefile from: <https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-2.688200%2C0.000000%2C1.41>

### task

The task this week is to:

-   Read in global gender inequality data
-   Join the global gender inequality index to spatial data of the World, creating a new column of difference in inequality between 2010 and 2019
-   Share it with the World on GitHub
-   Add you repository URL to the circulated spreadsheet

Tip the countrycode R package will be helpful!

Tip the gender inequality has changed in the last year, you will find what you need in the "All composite indices and components time series (1990-2021)" dataset, the metadata file beneath it will explain what the columns are.
- 在全球性别不平等数据中阅读
- 将全球性别不平等指数加入到《世界》的空间数据中，创建一个新的2010年和2019年之间的不平等差异列
- 在GitHub上与世界分享它
- 在分发的电子表格中加入你的存储库网址

提示 countrycode R包会有帮助!

提示性别不平等在去年发生了变化，你会在 "所有综合指数和成分时间序列（1990-2021）"数据集中找到你需要的东西，它下面的元数据文件会解释这些列是什么。
## Load packages

```{r}
# install.packages("countrycode")
```

```{r}
library(tidyverse)
library(sf)
library(here)
library(janitor)
library(countrycode)
```

```{r warning=FALSE}
# HDI读入的是世界206个国家性别不平等的指数，在1990-2021年
HDI <- read_csv(here::here("wk4_dataset", "HDR21-22_Composite_indices_complete_time_series.csv"),
                       locale = locale(encoding = "latin1"),
                       na = " ", skip=0)


# world读入.shp矢量表。有251个国家的长度，面积，地理坐标
World <- st_read(here::here("wk4_dataset", "World_Countries_(Generalized)", "World_Countries__Generalized_.shp"))

# 相对路径用 /连接
# World <- st_read("homework_4/World_Countries_(Generalized)/World_Countries__Generalized_.shp")
```

## Column names

Select columns we want and change country name to country code, using the `countrycode` package

We could also just join it without this on the country name column

Some notes:

-   COW codes = correlates of war codes
-   ISO = International Organization for Standardization with 2 or 3 letters...
选择我们想要的列并将国家名称改为国家代码，使用`countrycode`包

我们也可以不在国名列上这样做，直接加入它

一些说明。

- COW代码=战争代码的相关者
- ISO = 国际标准化国家名字的英文缩写，有2或3个字母...
```{r}
# HDI_mutate1<- HDI %>%
#   clean_names()%>%
#   select(iso3, country, gii_2019, gii_2010)%>%
#   mutate(difference=gii_2019-gii_2010)%>%
#   #not needed here as we can now use the country name...but see below
#   mutate(iso_code=countrycode(country, origin = 'country.name', destination = 'iso2c'))%>%
#   mutate(iso_code2=countrycode(iso3, origin ='iso3c', destination = 'iso2c'))
```


```{r}
HDIcols<- HDI %>%
  clean_names()%>%
  select(iso3, country, gii_2019, gii_2010)%>%
  mutate(difference=gii_2019-gii_2010)%>%
  #not needed here as we can now use the country name...but see below
   # 增加一列列名为iso_code，值为：将country列的name转换成iso2c的标准（两个字符）
   # 增加一列列名为iso_code2，值为：将iso3列转换成iso3c的标准（三个字符）
  # iso_code和iso_code2列的值一样
  mutate(iso_code=countrycode(country, origin = 'country.name', destination = 'iso2c'))%>%
  mutate(iso_code2=countrycode(iso3, origin ='iso3c', destination = 'iso2c'))

  
```

## Join

Join the csv to world shape file

```{r}
Join_HDI <- World %>% 
  clean_names() %>%
  left_join(., 
            HDIcols,
            by = c("iso" = "iso_code"))

# 261 if using "aff_iso", 251 if using "iso". Could filter out the NA values.因为用aff_iso=iso_code做左连接，aff_iso有十行都是na,连不上右表，但是会保留这aff_iso=na的十行
```

```{r}
# world仍然要clean_names()因为上面使用clean_names()时候并没有赋值world
Join_HDI_2 <- World %>% 
  clean_names() %>%
  left_join(., 
            HDIcols,
            by = c("country" = "country"))
#251

```

# Problems

-   With Join_HDI there are 11 rows for Antarctica if using aff_iso - be sure to use iso column or remove the NA values as in the aff_iso Antarctica is NA
-   With Join_HDI_2 the entries for other islands aren't joined as they don't have the same name...e.g. France, French Guiana, French Southern Territories.....
- 在Join_HDI中，如果使用aff_iso，南极洲有11行 - 确保使用iso列或删除NA值，因为在aff_iso中，南极洲是NA。
- 使用Join_HDI_2，其他岛屿的条目没有被加入，因为它们没有相同的名字......例如：法国，法属圭亚那，法属南方领土.....。

```{r}
Join_HDI_FR<-Join_HDI %>%
  filter(aff_iso=="FR")

Join_HDI_2_FR<-Join_HDI_2 %>%
  filter(aff_iso=="FR")
```

...next time we will make a map using different repos
